Barneby Lives usage example

### 2023-05-12 scripts/project_template.Rmd
prototype geomorpho grabber
evaluation with political

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 500), seq(1:500)),
  day = c(sample(1:31, size = 500, replace = T)),
  month = c(sample(5:10, size = 500, replace = T)),
  year = 2023,
  x = runif(500, min = -120, max = -100), 
  y = runif(500, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

out <- political_grabber(dummy_pts)
out <- place_grabber(dummy_pts)

rm(out)
# if within 0.5 km of place, use
# if dist > 0.5 km direct

>>>>

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 1000), seq(1:1000)),
  day = c(sample(1:31, size = 1000, replace = T)),
  month = c(sample(5:10, size = 1000, replace = T)),
  year = 2023,
  x = runif(1000, min = -120, max = -100), 
  y = runif(1000, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

out1 <- political_grabber(dummy_pts, 'collectionNo')
out2 <- place_grabber(dummy_pts)
out3 <- physical_grabber(dummy_pts)

out <- out1 %>% 
  dplyr::mutate(
    Gen = paste0(
      Country, ', ', State, ', ', County, ' Co., ', Mang_Name, " ", Unit_Nm, " ", trs), 
    Gen = stringr::str_replace_all(Gen, "NA", ""), 
    Gen = stringr::str_replace_all(Gen, "  ", ""))
